---
title: "Projects"
links:
 - text: https://sammytetrault.github.io
   href: https://sammytetrault.github.io
---

This semester at CSU (Spring 2025) I am taking ESS330, Quantitative Reasoning. In this course we are learning to use R and RStudio. We will be using R to do data analysis, as well as other projects, like this website!

Below are links to all of the projects I have completed in this course:

1\) Building a Personal Website: For this project, I created a quarto website and learned how to create a site with Github pages, link websites, and customize the theme. Check out my github linked on the home page to see the repository with all of the code for this.

<https://sammytetrault.github.io>

```{r, results = 'hide', echo = FALSE}

library(magick)

lab_1_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_1.jpg")

grid::grid.raster(lab_1_img)
```

2\) Minnesota Tree Growth (Using dplyr): For this lab, I learned how to use common dplyr functions like filter(), mutate(), and more to manipulate a dataset and summarize the data to answer questions about the data.

```{r, results = 'hide', echo = FALSE}

lab_2_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_2.jpg")

grid::grid.raster(lab_2_img)
```

3\) COVID-19 Data Wrangling: For this lab, I practiced using dplyr functions learned from the previous project and learned how to use new features like flextable.

```{r, results = 'hide', echo = FALSE}

lab_3_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_3.jpg")

grid::grid.raster(lab_3_img)
```

4\) Statistics in R: For this lab, I practiced running statistical tests like chi-square, t-tests, correlation tests, ANOVA, equal variance tests, etc. I also learned how to create a linear regression and multiple linear regression model and how to visualize tests and models.

```{r, results = 'hide', echo = FALSE}

lab_4_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_4.jpg")

grid::grid.raster(lab_4_img)
```

5\) Project Proposals: For this lab, I worked with a group in which we each created 2 project proposals for a project that we designed. I learned how to find data, form a research question and describe its significance, and plan statistical tests and preliminary methods.

```{r, results = 'hide', echo = FALSE}

lab_5_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_5.jpg")

grid::grid.raster(lab_5_img)
```

6\) Machine Learning Workflows: For this lab, I learned how to use a workflow and workflow set, build different types of models, compare and evaluate model performance, and visualize models.

```{r, results = 'hide', echo = FALSE}

lab_6_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_6.jpg")

grid::grid.raster(lab_6_img)
```

7\) Final Project Intro & Methods: For our final project, my partners and I decided to investigate the relationship between wolf populations in Yellowstone and prey species (bison and elk). For this lab, my partners worked on writing the introduction for our project, while I did exploratory data analysis and data cleaning to get our data in the right format to build models. I created visualizations of each population over time, ran a Shapiro-Wilk test and a QQ test to check normality, and created plots for these tests.

```{r, results = 'hide', echo = FALSE}

lab_7_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_7.jpg")

grid::grid.raster(lab_7_img)
```

8\) Final Project Results & Discussion: For this lab, I created 4 ARIMA models and 4 GLMs to investigate the relationship between wolf vs. bison populations, wolf vs. elk populations, bison vs. elk populations, and elk vs. bison populations, to see if one population could predict the other. Our strongest results were the models in which one prey population was used to predict the other, indicating that resource competition may be one of the largest limiting factors for prey species.

```{r, results = 'hide', echo = FALSE}

lab_8_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_8.jpg")

grid::grid.raster(lab_8_img)
```

9\) Distances and Projections: For this lab, I learned how to use spatial data in R. I learned how to get spatial data using the AOI package, how to manipulate spatial features using functions like st_union() and learned how to visualize spatial data using ggplot and ggrepel.

```{r, results = 'hide', echo = FALSE}

lab_9_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_9.jpg")

grid::grid.raster(lab_9_img)
```

10\) Lightening Talk: For this lab, my final project group delivered a lightening talk about our project, including background, methods, plots, results, and conclusions. I learned how to convey data and findings to an audience that may have been unfamiliar with the topic, models, or statistics used.

```{r, results = 'hide', echo = FALSE}

lab_10_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_10.jpg")

grid::grid.raster(lab_10_img)
```

11\) Spatial Data: For this project, I used a shp file of major world rivers and a county boundaries object accessed through the AOI package to find counties that intersect the Mississippi River system. I practiced using functions like st_filter() and st_join and created a map using ggplot.

```{r, results = 'hide', echo = FALSE}

lab_11_img <- image_read("C:/Users/sammy/OneDrive/Desktop/ESS330/sammytetrault.github.io/img/img_lab_11.png")

grid::grid.raster(lab_11_img)
```
